\Title

### 2016-02-10 manuscript/manuscript.tex
Figure for model and data in simple synthetic

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figures/synthetic-simple-data}
    \caption{
        A simple Moho model made of tesseroids for synthetic data application.
        (a) The Moho depth of the model in kilometers.
        The model transitions from a deep Moho in the right to a shallow Moho in
        left, simulating the transition between a continental and an oceanic
        Moho.
        Each pixel in the pseudo-color image corresponds to a tesseroid of the
        model.
        (b) Noise-corrupted synthetic gravity data generated from the model
        shown in (a).
    }
    \label{fig:simple-data}
\end{figure}
